%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Data Scientist II} % Job title
{Nike, Inc.} % Organization
{Beaverton, OR (Remote)} % Location
{Mar 2022 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {
Led effort to architect and develop Fulfillment Optimization (FO) simulation, generating 11\% increase in annual savings in NA or \$50M total EBIT in FY23, by using Python, Flask, ORTools, and PostgreSQL to allow for back-testing with 99\% similarity to production.
}
\item {
Spearheaded the value measurement for our team by designing a baseline, estimating FY23 savings with 8\% decrease in shipping costs while using 40\% less CO2 annually, through analysis with SQL, Pandas, and Snowflake.
}
\item {
Collaborated with lead data scientists to build a simpler and more powerful decision engine that satisfied all previous requirements and reduced shipping inefficiencies by 2\%, with an ORTools/Gurobi optimization model.
}
\item {
Integrated FO from NA to EMEA, enabling cost-saving strategies that saved approximately 5M€ for FY23 by altering our Python code-base, SQLAlchemy schemas/queries and building new algorithms.
}
\item {
Enabled Kubernetes/EKS distributed system to support horizontal scalability, facilitating the simultaneous execution of multiple experiments and scaling workers for each experiment. Generalized the codebase to enable local testing, debugging, and seamless integration with CI/CD pipelines.
}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Machine Learning Engineer} % Job title
{Solution Consulting Group, LLC} % Organization
{Knoxville, TN (Remote)} % Location
{Aug 2021 - Jan 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Introduced an automated ML solution to replace a subjective grading process, reducing a manual 2 minutes per card grading process by 40\% while also providing segmentation masks for surface damages.}
\item {Transformed thousands of unlabelled 100MP images into training data that produced a MVP model, a UNet semantic segmentation classifier implemented with PyTorch and deployed with TorchServe and SageMaker.}
\item {Presented AI/ML solution to non-technical stakeholders, visualizing our approach as a black-box technique for describing surface damages in a card.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Scientist} % Job title
{The Hartford} % Organization
{Hartford, CT (Remote)} % Location
{Jun 2020 - Aug 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Improved error on auto insurance premium predictions by 5\% with distributed frameworks PySpark and H2O, utilizing a XGBoost model on top of a GLM and validating results with K-fold cross-validation.}
\item {Illustrated insights on potential improvements by different car manufacturers to visualize where current GLM under-performs.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{CoreLogic, Inc.} % Organization
{Irving, TX} % Location
{Jun 2019 - Aug 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented an internal web application for requesting access within the company that improved on a one-by-one request process to a batched one with Test-Driven Development in Angular, JavaScript, Java and Spring Boot.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}